\problemchapter{Introduction}
\label{chap:introduction}

Blockchain technology has emerged as a revolutionary force, reshaping industries with its promise of decentralization, transparency, and security. However, the journey towards seamless blockchain interoperability and user-friendly experiences is still ongoing. This paper presents an innovative solution, the Sapphire Wallet, which has been developed by Manuele Nolli as part of his Master of Science in Engineering (MSE).

The project's ambitious goal is to explore the state of the art in Blockchain technology and create a decentralized wallet that empowers users to effortlessly interact with multiple blockchains. 

\textit{Account Abstraction} promises to enhance user experience by abstracting the complexities of blockchain accounts, while \textit{Cross-Chain Communication} aims to solve the interoperability challenges between different blockchains. This paper reviews the most significant Ethereum Improvement Proposals (EIPs) and leading projects in these domains.

The project includes the development of a decentralized wallet called \textit{Sapphire Wallet} that allows users to benefit from the \textit{Account Abstraction} and \textit{Cross-Chain Communication} features. The infrastructure of the wallet is largely explained in the paper.

In the final part of the paper, the results and conclusions of the project are presented. The world adoption of Blockchain technology is not yet a reality, but the \textit{Sapphire Wallet} is a step forward in this direction. This project highlights the potential of current Blockchain advancements and underscores the need for continuous innovation and protocol evolution to fully realize the decentralized future.