\chapter{Problem Approach: Sapphire Wallet}
\label{chap:problem_approach}

In this chapter, The Sapphire Wallet ecosystem is presented. The Sapphire Wallet is a Multi-Chain Account Abstraction, based on an improved version of the \hyperref[subsec:argent]{Argent Wallet}.

Sapphire Wallet is a Proof of Concept of the future of Blockchain technology. The main goal of Sapphire Wallet is to give an idea of the potential of the Blockchain technology in combination with Account Abstraction Layer and Multi-Chain Bridge approach. To achieve this goal, the Sapphire Wallet includes a set of features already present in the Argent Wallet, such as guardian, wallet creation and wallet recovery. Moreover, the Sapphire Wallet ecosystem includes a Multi-Chain Bridge, which allows the user to interact with different Blockchains. 

It is important to notice that the Sapphire Wallet is developed on the current version of EVM\footnote{Dencun version}. There are several promising \hyperref[subsec:eips]{EIPs} that could be implemented in the future, such as the \hyperref[subsubsec:eip-3074]{EIP-3074} and the \hyperref[subsubsec:erc-7702]{EIP-7702}, but they need an hard fork of the Ethereum network. Whatever the final Account abstraction implementation is, the Sapphire Wallet provides a realistic Proof of Concept of how the users will interact with the Blockchain in the future.

In the following sections, the architecture and the components of the Sapphire Wallet ecosystem are presented. Each section is described in isolation, but at the end of the chapter, the operational flow and the use cases are presented to give a complete overview of the Sapphire Wallet functionalities.

\input{content/problem_approach/architecture}
\input{content/problem_approach/blockchain}
\input{content/problem_approach/bridge}
\input{content/problem_approach/backend}
\input{content/problem_approach/mobile_application}

\input{content/problem_approach/operational_flow_and_use_cases}