\section{Mobile Application: Sapphire Wallet}
\label{sec:mobile_application}

The Sapphire Wallet Mobile App is the main component of the Sapphire ecosystem. It is the interface that enable the users to interact seamlessly with the Blockchain. Indeed, it enables the users to manage their assets and perform transactions on multiple Blockchains without the need to know anything about the Blockchain technology.

The Mobile App maintains securely saved an External Owned Account keys, which are used to sign transactions that are then sent to the \hyperref[sec:backend]{Backend} to be forwarded to the \textit{Base Chain}. Each time a user wants to perform an action, the Mobile App will ask a biometric authentication to sign the transaction. The EOA keys are important because the grant the user the ownership of the \textit{Proxy} contract well described in the \hyperref[subsec:base_chain]{\textit{Base Chain}} section. But, in the case of loss of the EOA keys, the user can recover its wallet by using the \hyperref[subsec:wallet_recovery]{Wallet Recovery} process.

Sapphire Wallet is composed of three main pages:
\begin{itemize}
    \item \textit{Home Page}: Dynamically rendered based on the user's assets. It displays the user's balance for each chain, and provides buttons to perform transactions as \textit{Send Crypto / NFTs}.
    \item \textit{NFTs Page}: Displays the user's NFTs by highlighting which blockchain they are stored on.
    \item \textit{Settings Page}: Allows the user to manage their preferences, settings and guardians. 
\end{itemize}

In addition to these pages, the Sapphire Wallet also provides the functionality to create a new wallet or recover an existing one at the first launch.

The framework used to build the Sapphire Wallet is \textit{Expo}\footnote{https://expo.dev/}, which allows for the development of cross-platform applications. In fact, the Sapphire Wallet is available for both Android and iOS devices.

\subsection{Wallet Creation}
\label{subsec:wallet_creation}

\subsection{Wallet Recovery}
\label{subsec:wallet_recovery}

\subsection{Home Page}
\label{subsec:wallet_home_page}

Write all the operations, balance of chains, button.

\subsection{NFTs Page}
\label{subsec:nfts_page}

\subsection{Settings Page}
\label{subsec:settings_page}

guardian
